\section{Introduction}
\label{sec:intro}

An agent calls \texttt{search\_flights}. The registry contains
\texttt{find\_flights}. The call fails. Practitioners hit this mismatch
in production with Claude, Gemini, and Grok~\citep{czapla2026}, and what
stings is that the model knew the task, picked something plausible, and
just got the name wrong. The reflex fix is to hand the model the registry
--- show it the menu and it will order off it. We find the menu is mostly
decoration. What clears the failure is the \emph{shape} of the rejection,
not its contents: a structured \texttt{tool\_not\_found} envelope
re-grounds the model whether or not it lists a single real tool. We call
this format-not-content recovery, and it is the spine of this paper.

The framing has a pedigree. Min et al.\ showed that in-context
demonstrations help even when their labels are wrong --- the format
carries the signal, the content rides along~\citep{min2022rethinking}. We
report the reactive-recovery analogue: a registry-miss re-prompt fixes
tool-name fabrication even when the listed registry is empty
($\mathrm{C}_{0.7}$) or actively wrong ($\mathrm{C}_{0.8}$). Existing
benchmarks measure related quantities at the wrong grain.
API-Bank~\citep{li2023apibank} reports per-task name-mismatch up to
$61.4\%$ on a 2023-vintage model set;
MetaTool~\citep{huang2024metatool} isolates fabrication via target
removal and scores per-query Correct Selection Rate on single-turn
prompts; RelyToolBench~\citep{cao2025reliability} folds
non-existent-tool invocations into a composite reliability number. Read
together, the failure looks architecture-agnostic and uniform. We don't
think it is, and we don't think the fix is what it looks like either.

We define the per-call \emph{Tool Fabrication
Rate} (TFR) and run it over two populations on BFCL
multi-turn: the Anthropic 4.x family at five versions spanning
May~2025 to April~2026 (Opus~4.7, Sonnet 4/4.5/4.6, Haiku~4.5), and
Qwen3-Instruct at six sizes ($0.6$B--$32$B) in 4-bit MLX on
consumer hardware. Both see three BFCL splits plus a four-distractor
probe with the real target removed and a synthetic look-alike in
its slot. BFCL is strictly typed, so this isn't production, but it
is the closest we could get to Czapla's setting on a benchmark.
Figure~\ref{fig:scaling} is the headline.

Why a per-call existence rate matters: a fabricated name is not just a
failed call, it is an attack surface. \citet{spracklen2025packages}
audited package hallucinations in code-generating LLMs and found
open-source models invent non-existent dependencies at $\sim\!21.7\%$
against $\sim\!5.2\%$ for commercial ones---an open-vs-closed gap that
mirrors the Qwen-vs-Anthropic split we report, and one an adversary can
turn into ``slopsquatting'' by registering the hallucinated name and
waiting for the model to reach for it. Tool registries are the same
shape of target: an agent that confidently calls \texttt{find\_flights}
when only \texttt{search\_flights} exists is, in a registry an attacker
can write to, one fabrication away from invoking a planted look-alike.
We do not demonstrate that exploit here and make no exploitation claim;
we measure existence hallucination at the per-call grain precisely
because that is the unit at which such a risk would accrue.

The two families don't look alike. Across $2{,}599$ Anthropic calls
under $\mathrm{C}_0$, zero TFR events (Clopper--Pearson 95\% upper
bound $\leq\!0.115\%$); the $\mathrm{C}_1$ subset adds $0/678$ at
$\leq\!0.441\%$. Commercial models across the OpenAI gpt-4.1 and
gpt-4o tiers also log $0\%$ TFR ($0/404$, $0/408$, $0/409$, $0/419$,
$0/430$ for gpt-4.1, gpt-4.1-mini, gpt-4.1-nano, gpt-4o, gpt-4o-mini;
per-model upper bounds $\leq\!0.69$--$0.74\%$, $0/2{,}070$ pooled at
$\leq\!0.14\%$). The split designed to coax fabrication,
\texttt{multi\_turn\_miss\_func}, didn't bite: the agent chained
five smaller in-registry calls instead of inventing a one-shot.
With every Anthropic cell at $0/N$, no temporal slope is fittable;
the five versions function as a stability check, not a trend.

Qwen3 looks nothing like that. Pooled per-call rates climb from
$0\%$ at $0.6$B through $0.95\%$, $1.33\%$, $1.46\%$, peak at
$\mathbf{1.87\%}$ at $14$B, and drop back to $0\%$ at $32$B
($N\!=\!224$, consistent with any true rate $\leq\!1.33\%$). The
\emph{type} of distractor that wins also moves: $1.7$B peaks on
near-name ($3.7\%$); $4$B on matched-random ($5.4\%$); $8$B on
matched-random ($2.3\%$); $14$B on synonym ($7.2\%$). The bump is not noise. A generative
tool-name prior that strengthens with scale before a larger model's
registry-grounding control catches up predicts exactly this shape ---
a U-shaped capability window~\citep{wei2022ushaped,mckenzie2023inversescaling}.
The $0\%$ endpoints at $0.6$B and $32$B bracket the $1.87\%$ peak at
the same 4-bit MLX precision, so quantization is held fixed across the
arc; the curve is a capability effect, not a compression artifact. Six
points still isn't a curve, and we say so --- but it is the shape the
format-not-content account predicts. A cross-family release covering
six additional open models is in the supplement.

Registry-Visible Reprompting (RVR) is what we built to fix this.
The middleware is training-free: intercept the proposed call, check
the name, and on a miss re-prompt with a structured
\texttt{tool\_not\_found} envelope listing what is available. Across
the four Qwen3 tiers with non-zero TFR ($1.7$B, $4$B, $8$B, $14$B),
RVR clears all fourteen pooled fabrications: Fisher's exact one-sided
on $14/973$ vs.\ $0/945$ gives $p=7.1\!\times\!10^{-5}$. A
content-matched ablation ($\mathrm{C}_{0.7}$, $0/448$ on Qwen3-8B,
$\leq\!0.67\%$), keeping the envelope structure but dropping the registry list, also
hits zero --- and a decoy that fills the envelope with \emph{wrong}
names ($\mathrm{C}_{0.8}$) still logs zero. The envelope is doing the
work, not the listed names. On the Anthropic zero-event regime RVR holds at
zero, but strict-pass slips (Sonnet $60\!\to\!53/60$; Haiku
$60\!\to\!56/60$); a Newcombe-hybrid TOST at $N\!=\!60$ is
underpowered for a $5$-pp non-inferiority margin, so we can't rule
the cost in or out. We argue for tier-conditional deployment.

The Anthropic $\mathrm{C}_0$ bound ($\leq\!0.115\%$ at $N=2{,}599$)
sits an order of magnitude below the Qwen3 point estimates in the
$0.95$--$1.87\%$ band. The bound-vs-estimate asymmetry is the
finding. The intra-family non-monotonic shape on Qwen3 is itself
descriptive evidence aggregate metrics couldn't have surfaced. What we
give a deployer is concrete: (i) a per-call diagnostic that exposes
existence failures production guardrails silently absorb, (ii) the
format-not-content finding --- recovery rides on the rejection envelope,
not the registry it echoes --- and (iii) the deployable takeaway that
falls out of it: ship the structured envelope, and you need not leak your
registry to get the fix. We release four artifacts: the per-call TFR
diagnostic, an eleven-model audit over eleven months, RVR with per-tier
validation, and an open-source harness with $144$ unit tests. Total API
spend \$$73$; the Qwen3 sweep ran at zero marginal cost on the M5.
