\section{Method}
\label{sec:method}

\subsection{Tool Fabrication Rate (TFR)}
\label{sec:method:tfr}

Let a tool registry $\mathcal{R}$ be a finite set of tool names with JSON schemas, exposed to the agent at episode start. The agent's message stream is parsed into a sequence of tool calls $c$, each carrying a name $c.\mathrm{name}$, and we define
\[
\mathrm{TFR}(m, b, x) = \frac{|\{c : c.\mathrm{name}\notin \mathcal{R}\}|}{|\{c : c \text{ is a parsed tool call}\}|},
\]
where $m, b, x$ index model, benchmark, and condition. The denominator is per call, not per task. Per-task aggregation conflates the rate with trace length: on long tool-using episodes, a single bad agent emitting twenty bad calls swings the headline number by an order of magnitude relative to one. Per-call observations inside a task are not assumed i.i.d.; task-level cluster-bootstrap confidence intervals are reported instead. System failures (timeout, refusal, parse-fail) are excluded from numerator and denominator alike.

\subsection{Registry-Visible Reprompting (RVR)}
\label{sec:method:rvr}

RVR is a single-turn intervention placed between the agent and the tool executor (Appendix Figure~\ref{fig:rvr-arch}). On a membership-violating call, it returns a re-prompt that names the offending call and lists the available tools:

\begin{lstlisting}[language=Python,basicstyle=\ttfamily\footnotesize]
def rvr(agent_msg, registry):
    proposed = parse_tool_call(agent_msg)
    if proposed.name not in registry:
        return Action.RE_PROMPT(
            f"Tool '{proposed.name}' not in registry. "
            f"Available: {sorted(registry.keys())}.")
    return Action.EXECUTE(proposed)
\end{lstlisting}

Echoing $\mathcal{R}$ back into the conversation places valid names in the model's recent context, which is what the next decoding step attends to. The intervention uses one re-prompt, a production-realistic budget; it is training-free and assumes no gradient access; it composes with RL-based methods such as Fission-GRPO~\citep{fissiongrpo2026}; and it is the message-level analog of constrained decoding for closed-API regimes without logit access.

\subsection{Conditions and the content-vs-format question}
\label{sec:method:conditions}

Five conditions are run on a hallucinated call. \textbf{$\mathrm{C}_0$} is the
opaque baseline, returning the framework's default error string.
\textbf{$\mathrm{C}_{0.5}$} is a naive retry with the literal text ``previous
call failed, try again''. \textbf{$\mathrm{C}_{0.7}$} is a structured error,
JSON \texttt{\{"error":"tool\_not\_found"\}}, with no registry attached.
\textbf{$\mathrm{C}_1$} is RVR proper (Section~\ref{sec:method:rvr}): the
structured envelope \emph{plus} the sorted real registry. \textbf{$\mathrm{C}_{0.8}$}
holds the $\mathrm{C}_1$ envelope prose verbatim but swaps the listed tools for a
count-matched \emph{decoy} set guaranteed absent from the registry. The ladder
is built so that adjacent steps isolate one factor each: $\mathrm{C}_{0.7}\!:\!\mathrm{C}_{0.5}$
isolates structure, $\mathrm{C}_1\!:\!\mathrm{C}_{0.7}$ isolates the presence of a list,
and $\mathrm{C}_1\!:\!\mathrm{C}_{0.8}$ isolates whether the listed names must be
\emph{correct}. At scale we report the conservative $\mathrm{C}_1\!:\!\mathrm{C}_0$.

We do not try to localize the effect to a specific cognitive story. An
earlier draft pre-registered three mechanisms (induction-head copying,
registry-as-cue, message-level rejection); the data cannot separate
copying from cueing, so we drop that apparatus rather than over-read it.
What the design is \emph{aimed at} is a single binary: does recovery
require the registry \emph{content}, or only the rejection \emph{format}?
If a wrong list ($\mathrm{C}_{0.8}$) re-introduces fabrications where the
real list ($\mathrm{C}_1$) does not, the model is reading the offered
names; if neither arm fabricates, the comparison bounds the content
effect rather than settling it (Section~\ref{sec:mechanism}), and
distinguishing the two requires fabrication events under the ablation. The
distractor probe (Section~\ref{sec:method:probe}) is retained to
characterize \emph{where} on the scale curve fabrications concentrate,
not as a mechanism discriminator.

\subsection{Distractor-Type Probe}
\label{sec:method:probe}

One distractor is injected into $\mathcal{R}$ on tasks where $\mathrm{C}_0$ already passes, with its type varied to characterize which kind of look-alike concentrates fabrications (Appendix Figure~\ref{fig:probe}). \textbf{near\_name} draws a string at Levenshtein distance 1 or 2 from a real target. \textbf{synonym} is high embedding-cosine but Levenshtein-far: semantic but not orthographic overlap. \textbf{matched\_random} is lexically random, matched to the real target on description length and arity, controlling for the ``registry-size $+1$'' confound. \textbf{unrelated} is lexically and semantically disjoint, the floor case. To capture the Czapla-style runtime collision, the real target is also removed and the distractor placed in its slot: the agent expects a tool that exists, but the registry offers only a similarly-named substitute.
