\section{Experimental Setup}
\label{sec:setup}

\textbf{Models.}~We evaluate two populations. The Anthropic 4.x
family (Opus~4.7, Sonnet 4/4.5/4.6, Haiku~4.5) is queried through
the provider's tool-use API at \texttt{temperature=0}, with rolling
aliases resolved at run-start to dated snapshots and pinned in the
manifest. The Qwen3-Instruct family (0.6B, 1.7B, 4B, 8B, 14B, 32B)
runs locally as \texttt{mlx-community} 4-bit MLX builds on an
Apple~M5 with $32$~GB unified memory, macOS~15. The manifest lists
SDK and dataset pins. A supplementary cross-family release covers
six additional open models: Llama-3.1-8B, Mistral-7B-v0.3,
Gemma-2-9B, Qwen2.5-7B, Phi-3.5-mini, and
DeepSeek-R1-Distill-Qwen-7B. Both populations decode greedy.

\textbf{Benchmark.}~All experiments run on BFCL v4 multi-turn,
using three splits: \texttt{multi\_turn\_base} (aligned registry),
\texttt{multi\_turn\_miss\_func} (one required tool removed), and
\texttt{multi\_turn\_long\_context}. The distractor probe runs on
$N\!=\!15$ \texttt{multi\_turn\_base} tasks where the opaque
baseline already passes. For each task we remove the real target
tool and inject one synthetic distractor in its slot.
Table~\ref{tab:coverage} reconciles which model saw which split: the
``five Anthropic versions across eleven months'' breadth lives on
\textsc{base} only, the three-split regime sweep is two production
models plus one local model, and the per-cell counts sum to the pooled
$0/2{,}599$ Anthropic figure.

\newcommand{\pmark}{\ensuremath{\bullet}}
\newcommand{\rmark}{\ensuremath{\circ}}
\begin{table}[t]
\caption{Model $\times$ BFCL-split coverage. Cells are no-intervention (C0)
calls; a glyph marks the experiment design that produced them. \pmark{}: the
five-distractor probe grid (target removed, per-call existence scored).
\rmark{}: the regime cell from the main grid. The ``five Anthropic versions
across eleven months'' claim holds on \textsc{base} only; the three-split regime
sweep is two production models (Haiku 4.5, Sonnet 4.6) plus one local model
(Qwen3-8B, base). Anthropic hallucinated $=0$ in every cell; the per-call
\textsc{tehr} signal is the Qwen3 size sweep on \textsc{base}.}
\label{tab:coverage}
\centering
\small
\setlength{\tabcolsep}{5pt}
\begin{tabular}{lccc}
\toprule
 & \multicolumn{3}{c}{BFCL split (C0 calls)} \\
\cmidrule(lr){2-4}
Model (version) & base & long-ctx & miss-func \\
\midrule
\multicolumn{4}{l}{\emph{Anthropic 4.x}} \\
Sonnet 4.0 \scriptsize(05/2025)   & \pmark\,253 & --          & --          \\
Sonnet 4.5 \scriptsize(09/2025)   & \pmark\,285 & --          & --          \\
Sonnet 4.6                        & \pmark\,677 & \rmark\,81  & \rmark\,128 \\
Opus 4.7                          & \pmark\,293 & --          & --          \\
Haiku 4.5                         & \pmark\,655 & \rmark\,107 & \rmark\,120 \\
\midrule
\multicolumn{4}{l}{\emph{Qwen3 size sweep (4-bit)}} \\
0.6B   & \pmark\,75   & -- & -- \\
1.7B   & \pmark\,210  & -- & -- \\
4B     & \pmark\,226  & -- & -- \\
8B     & \pmark\,615  & \multicolumn{2}{c}{\rmark\,108 (base regime)} \\
14B    & \pmark\,268  & -- & -- \\
32B    & \pmark\,224  & -- & -- \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Statistics.}~TEHR is per parsed tool call. Per-cell rates
get Clopper--Pearson upper bounds; non-zero cells get a BCa cluster
bootstrap (10{,}000 resamples, clustered by task). Pooled
$\mathrm{C}_0$ vs.\ $\mathrm{C}_1$ uses Fisher's exact one-sided.
Distractor-type effects use Friedman with Nemenyi post-hoc, and
non-inferiority uses TOST at a 5-pp margin. We apply
Holm--Bonferroni across the three primary tests. System failures
(timeout, parse failure, refusal) are excluded from both numerator
and denominator, and tracked separately.

\textbf{Reproducibility.}~A \texttt{repro\_manifest.json} pins the
BFCL v4 commit, SDK versions, dated model aliases, decoding
parameters, and random seeds (master seed $42$). Distractor
injection uses SHA-256 truncation, so reproduction does not depend
on \texttt{PYTHONHASHSEED}. The supplementary archive at
\href{https://anonymous.4open.science/r/icml-tehr-scale-2026/}{anonymous.4open.science/r/icml-tehr-scale-2026}
holds the harness, $144$ unit tests, the JSONL trace logs, and
the aggregation and statistics scripts that regenerate every
numerical claim in the paper, including Fisher's
$p\!=\!7.1\!\times\!10^{-5}$.
