\section{What recovers: content or format}
\label{sec:mechanism}

Does recovery use the \emph{content} of the echoed registry, or only the
\emph{format} of a structured rejection? The condition ladder speaks to
this, though, as we stress below, it bounds the content effect rather
than resolving it, because every arm is zero-event.

\paragraph{The ablation is suggestive, not decisive.}
On Qwen3-8B the structured error $\mathrm{C}_{0.7}$, a
\texttt{tool\_not\_found} envelope with \emph{no registry attached}, also
drives fabrications to zero, matching full RVR
(Section~\ref{sec:results:rvr}). If the model needed to \emph{read} the
registry to recover, removing it might cost something; within this
experiment's resolution we see no such cost. But both arms are
zero-event, so this bounds rather than excludes a content contribution.

\paragraph{The decoy arm sharpens, but does not close, the question.}
$\mathrm{C}_{0.7}$ removes the list; it does not test a list present but
\emph{wrong}. A registry-as-cue account predicts a decoy list (correctly
formatted, count-matched, but populated with non-existent tools) should
fail to recover, with no valid name to copy. A format-only account
predicts it recovers anyway, since the constraint ``your last call was
rejected; choose from this set'' need not be truthful to suppress the
out-of-registry call. The $\mathrm{C}_{0.8}$ condition runs this contrast:
the $\mathrm{C}_1$ envelope prose held verbatim, only the listed names
swapped for guaranteed-absent decoys.

The decoy list logs $0/410$ (Clopper--Pearson 95\% two-sided upper bound
$\leq\!0.90\%$) across all four probe arms (near\_name $0/97$, synonym
$0/106$, matched\_random $0/107$, unrelated $0/100$), matching the
no-list envelope ($\mathrm{C}_{0.7}$, $0/448$) and the real list
($\mathrm{C}_1$, $0/258$ on 8B). All three arms are zero-event, so we
\emph{detect no content effect at this sample size}: absence of
evidence, not evidence of equivalence. The
$\mathrm{C}_1\!-\!\mathrm{C}_{0.7}$ difference is bounded by a Newcombe
95\% CI of $[-1.5, +1.4]$~pp, and $\mathrm{C}_1\!-\!\mathrm{C}_{0.8}$
similarly; these are consistent with the registry content buying up to
$\sim$1~pp of recovery, not with it buying nothing. The data are thus
\emph{compatible with} a format-over-content account, the model
responding to the message-level rejection rather than the valid names
offered, but we do not treat zero-vs-zero as proof, and a
registry-as-cue account is not ruled out within the $\pm$1.5~pp band.

We settle it on a high-event cell. Qwen2.5-7B opens at
$\mathrm{C}_0=6.10\%$, $28$ real fabrications to suppress, and
Table~\ref{tab:qwen25-ablation} walks the ladder down. All three
envelope arms collapse the rate far below $\mathrm{C}_0$ (Fisher,
$p<10^{-3}$) and none differs from another (pairwise Fisher $p>0.37$);
the \emph{wrong}-list arm matches the real-list arm exactly
(Fisher $p=1.0$). With events available to recover, the content effect
the $\pm$1.5~pp Qwen3-8B bound left open does not appear. This is a
\emph{powered} null on content: a registry of \emph{wrong} names (or no
list at all) recovers as well as the right one. A bare retry helps but
less, leaving a residual $\sim\!5\times$ the structured arms, though that
retry-vs-envelope gap is only suggestive at this $N$ (Fisher vs.\
$\mathrm{C}_1$, $p=0.09$).

\begin{table}[t]
\caption{Qwen2.5-7B recovery ladder on the $\mathrm{C}_0$ target-removed
probe. Cells are events\,/\,parsed calls. Every structured arm collapses
the rate (Fisher $p<10^{-3}$ vs.\ $\mathrm{C}_0$); the arms do not differ
from one another (pairwise $p>0.37$), and a \emph{wrong} registry recovers
exactly as well as the real one ($\mathrm{C}_{0.8}$ vs.\ $\mathrm{C}_1$,
Fisher $p=1.0$).}
\label{tab:qwen25-ablation}
\centering
\small
\setlength{\tabcolsep}{5pt}
\begin{tabular}{llcl}
\toprule
Condition & Events\,/\,$N$ & TFR & Takeaway \\
\midrule
$\mathrm{C}_0$ (opaque)        & $28/459$ & $6.10\%$ & baseline \\
$\mathrm{C}_{0.5}$ (retry)     & $7/410$  & $1.71\%$ & partial \\
$\mathrm{C}_{0.7}$ (no list)   & $4/412$  & $0.97\%$ & recovers \\
$\mathrm{C}_{0.8}$ (wrong list)& $1/405$  & $0.25\%$ & recovers \\
$\mathrm{C}_1$ (real list)     & $1/320$  & $0.31\%$ & recovers \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{What this does not claim.}
Format-sufficiency is a claim about \emph{recovery}, not task success. On
TFR alone RVR matches any structured rejection: a hard reject also
yields $0$ by construction. RVR's distinction is that it is
\emph{recovery-preserving}, returning the live registry so the agent can
re-select a valid tool instead of aborting. A decoy list suppresses the
fabricated call but offers no valid target, so where the real tool was
removed the model must still decline or redirect; the value of the
\emph{true} registry shows up in task-completion rate, not in TFR, the
quantity the rejection signal governs. Nor does format-sufficiency hold at
every scale: it is established only on tiers where C0 fabrications exist
to suppress (1.7--14B); the 0.6B and 32B tiers carry no signal to recover.

\paragraph{The scale curve, descriptively.}
The dominant distractor type drifts with scale
(Section~\ref{sec:results:scaling}), but a Friedman exact permutation test is
underpowered ($\chi^2_{(3)}\!=\!3.0$, $p\!=\!0.46$; $n\!=\!4$ sizes), so we read
the drift as phenomenology, not inference. The content-vs-format question rests
not on this matrix but on the $\mathrm{C}_{0.7}$/$\mathrm{C}_{0.8}$
ablations, powered on Qwen2.5 above: a wrong registry recovers as
well as the right one.
