\section{Discussion and Limitations}
\label{sec:limitations}
\label{sec:limitations:rvr-null}

\input{sections/_inbody_deployer}

Table~\ref{tab:deployer} condenses the tier-conditional recommendation
into one operator-facing artifact; the rest of this section states what
the audit does and does not license.

We cannot fully disentangle the Anthropic--Qwen3 gap: parameter count, training recipe, and provider guardrails co-vary, and commercial-vs-open still bundles the serving path with the weights. Quantization, however, is no longer a confound: a precision ladder (4-bit/8-bit/bf16) on Qwen3-8B shows fabrication persists at full precision (Section~\ref{sec:results:controls}), so it is not a quantization artefact, and a second open lineage (Llama-3.1-8B) reproduces the gap. The Anthropic zero-event regime is indistinguishable from BFCL v4 contamination, since v4 predates every model tested and we ran no paraphrase or membership-inference control. RVR's $20\!\to\!0$ prevention is invariant to quantization, as $\mathrm{C}_0$ and $\mathrm{C}_1$ share weights. On Anthropic, RVR is a call-path no-op yet strict-pass drops (Section~\ref{sec:results:rvr}), and our Newcombe-hybrid TOST is underpowered at $N\!=\!60$. We recommend $\mathrm{C}_{0.7}$/RVR only on tiers with audited $\mathrm{TFR}\!>\!0$, paired with executor-side allow-listing. Scope: the probe tests registry-shape, not runtime-shape (Czapla's \texttt{read\_secret()} collision needs ambient-reachability BFCL lacks); TFR ignores latency, abstention, and pass-rate; and we claim no scaling law. We do show the fabrication gap in a second open family (Llama-3.1-8B) and that RVR sharply reduces it there (to $0.41\%$, with both residual calls caught by the rejection layer rather than reaching the executor), but with only two open lineages, and a cross-family null looser than the per-tier-matched Qwen3 sweep, we do not claim general cross-family transfer. A second benchmark bounds the finding's reach rather than extending it. On $\tau$-bench---multi-turn, with a simulated user---the commercial null holds ($0/2{,}244$ pooled across gpt-4.1, Sonnet~4.6, and Haiku~4.5, $\leq\!0.16\%$), but our target-removed probe did not elicit open-weight fabrication: Qwen3-8B and 14B emitted $191$ valid in-registry calls with zero fabrications ($\leq\!1.91\%$) while completing none of the $24$ probed $\tau$ tasks. We read this as benchmark-structure dependence---$\tau$'s user-sim and larger task registries do not reproduce BFCL's clean ``expected tool absent'' pressure---and therefore scope the open-weight gap to BFCL-style target-removed registries, not to tool use in general. Because those $\tau$ tasks also went uncompleted, the null may reflect too little successful tool engagement to fabricate on rather than genuine robustness; we read $\tau$ as a scope boundary, not a negative result. Breadth is bounded by tooling for the same reason: four further open families (Mistral-7B-v0.3, Gemma-2-9B, Phi-3.5-mini, DeepSeek-R1-Distill-7B) emitted no parseable tool calls under our text-parse harness and yield no rate, so the open-weight evidence rests on the three lineages above (Qwen3, Qwen2.5, Llama).
