\appendix

\section{Pre-Registration and Reproducibility}
\label{sec:appendix:prereg}

The pre-registered protocol is locked in git commit \texttt{c391017},
dated before any data was collected. Three deviations from that
protocol are worth naming. Probe $N$ was reduced from $100$ to $15$
per cell to fund breadth across five Anthropic versions and six
Qwen3 sizes. The OpenAI gpt-4.1 and gpt-4o tiers were added to the
vendor scope after the pre-registration (five commercial models,
$0/2{,}070$ pooled C0 calls, all $0\%$ TFR); the gpt-5 family is
still in collection. $\mathrm{C}_{0.7}$
was run at scale on Qwen3-8B only, not on Anthropic. Holm--Bonferroni
correction across the three primary tests (Fisher's exact, Friedman,
TOST): only Fisher's clears $\alpha\!=\!0.05$ at
$p_{\mathrm{Holm}} = 2.14\!\times\!10^{-4}$.

% NUMBERS_TODO: the following experiments are still running and are NOT yet
% in scripts/aggregate_all.py; do not cite numbers until aggregated:
%   (1) gpt-5 family frontier rows (currently only gpt-5-mini at n=19, preliminary, 0/19);
%   (2) quantization-control cells: Qwen3-8B-8bit, Qwen3-8B-bf16, Qwen3-14B-8bit;
%   (3) A2 reflection arm (currently only n=30, preliminary);
%   (4) Qwen3-14B event-boost cell.

The supplementary repository at
\href{https://anonymous.4open.science/r/icml-tehr-scale-2026/}{anonymous.4open.science/r/icml-tehr-scale-2026}
contains the full harness ($144$ unit tests), the JSONL trace logs
that produce every number in the paper, the aggregator and statistical
scripts, the reproducibility manifest with dated model aliases, the
full deviation log, the JSONL trace schema, the headline-number
derivation rule, and a registry-size pilot. Running
\texttt{python scripts/aggregate\_all.py} on the released traces
reproduces every numerical claim. Distractor-injection RNG uses a
SHA-256-derived stable hash, so reproduction does not depend on
\texttt{PYTHONHASHSEED}; MLX 4-bit local inference is not
bitwise-deterministic across runs but per-task tool-call decisions
are stable to within $\pm 1$ token.
