% =====================================================================
% STAGED ARTIFACT 3/3 -- plus-page camera-ready (+1 page, limit 8, body <=8pp)
% response_to_reviewers.tex
% Purpose: the compact "Response to reviewer comments" block that is the
%          STATED reason the workshop grants the +1 page. Maps each main
%          criticism from the three accept-decision workshop reviews
%          (8/6/3, Accept-Poster) to the exact camera-ready change that
%          addresses it, citing our own sections by their LOCKED numbers.
%          Honest and concrete; what has landed is reported as landed,
%          what is in progress is flagged as in progress.
%
% LOCKED NUMBERS (verified vs scripts/aggregate_all.py) -- never change:
%   Anthropic pooled C0  0/2,592   <=0.14%
%   OpenAI pooled        0/2,117   <=0.18%
%   Qwen3-14B C0 peak    6/366  = 1.64%
%   Qwen3 curve  0.6B 0/75 | 1.7B 2/210 | 4B 3/226 | 8B 9/615 | 14B 6/366 | 32B 0/224
%   RVR headline         C0 20/1,417 vs C1 0/945, Fisher p = 3.5e-5
%   Ablation  C0.7 0/448 | C0.8 0/410 | C1 0/258 (Newcombe CI [-1.5,+1.4]pp)
%   Precision ladder (Qwen3-8B)  4-bit 9/623=1.44% | 8-bit 2/435=0.46% | bf16 2/316=0.63%
%   Cross-family  Llama-3.1-8B C0 5/400=1.25% | Llama C1 RVR 2/487=0.41%
%                 Qwen2.5-7B 28/459=6.10%
%
% STATE OF EACH CONTROL at camera-ready:
%   - Precision ladder: LANDED (Sec 5.5, Table controls). Fabrication
%     persists at bf16 -> NOT a quantization artefact. Report as done.
%   - Cross-family: LANDED. Llama-3.1-8B + Qwen2.5-7B reproduce the gap;
%     RVR generalizes (Llama 1.25% -> 0.41%, residuals caught by the
%     rejection layer). Report as done; two lineages, NOT general transfer.
%   - tau-bench: gap test underway, wired + smoke-checked only. NO
%     paper-ready pass-rate -- report as in progress, no second site claim.
%   - Contamination: still open (Sec 7). Report as bounded caveat.
%   - Powered content-vs-format ablation on a high-event cell: in progress.
%
% INTEGRATION: place LAST in the body, after \input{07_limitations} and
%   before \input{08_llm_disclosure}, as an unnumbered section. Uses only
%   booktabs (\toprule/\midrule) + standard ICML packages. Single column.
% =====================================================================

\section*{Response to Reviewer Comments}
\label{sec:response}

We thank the three reviewers (scores 8/6/3) for the accept decision and
for criticism that was unusually concrete. This camera-ready page records,
point by point, how each load-bearing concern is addressed. Where a control
has landed since submission we say so and cite it; where work is still
running we flag it as in progress rather than soften it. We changed no
headline number: every figure below is regenerated by
\texttt{scripts/aggregate\_all.py} and pinned in the manifest.

\paragraph{R1/R2/R3: the $4$-bit quantization confound (the sharpest
objection, raised by all three).}
At submission the entire Qwen3 curve ran at $4$-bit MLX, and a reviewer
could fairly read the non-monotone shape as compression damage rather than
a capability effect. We have now run the deciding control: a precision
ladder on Qwen3-8B at $4$-bit, $8$-bit, and bf16 on the same
$\mathrm{C}_0$ target-removed probe (Section~\ref{sec:results:controls},
Table~\ref{tab:controls}). \textbf{Fabrication does not vanish at full
precision}: bf16 logs $2/316\!=\!0.63\%$ alongside $8$-bit
$2/435\!=\!0.46\%$ and $4$-bit $9/623\!=\!1.44\%$. The point estimates trend
downward as precision rises, but all three Clopper--Pearson intervals
overlap, so we claim no precision effect---only the load-bearing floor:
tool fabrication persists at bf16 and is therefore \emph{not} a
quantization artefact. We have removed every ``capability-not-compression''
assertion from the body and read the scaling shape descriptively; the one
claim that is confound-free regardless---RVR's $20\!\to\!0$ prevention
holds weights fixed between $\mathrm{C}_0$ and $\mathrm{C}_1$---is noted in
Section~\ref{sec:limitations}.

\paragraph{R1/R2: single open family / limited external validity.}
At submission the non-zero band rested on Qwen3 alone, leaving the gap
indistinguishable from a Qwen-lineage artefact. We have added two
independent open lineages on the same probe
(Section~\ref{sec:results:controls}, Table~\ref{tab:controls}).
Llama-3.1-8B-Instruct, which shares no lineage with Qwen, fabricates at
$5/400\!=\!1.25\%$---squarely inside the Qwen-family band---and
Qwen2.5-7B-Instruct fabricates at $28/459\!=\!6.10\%$, higher than any
Qwen3 size at any arm. The open-weight gap now appears in two distinct
lineages, not one. RVR generalizes across the family boundary, though not
to a clean zero: the $\mathrm{C}_1$ registry-visible re-prompt cuts
Llama-3.1-8B from $1.25\%$ to $2/487\!=\!0.41\%$ (a roughly threefold
reduction), and both residual emissions were intercepted by RVR's
\texttt{tool\_not\_found} rejection layer rather than reaching the
environment---so both RVR stages fire outside Qwen even where the prompt
alone leaves a residue. We are deliberate about scope: two open lineages
do \emph{not} establish general cross-family transfer
(Section~\ref{sec:limitations}), and the cross-family null is weaker than
the per-tier-matched Qwen3 sweep ($0/945$), as expected for a single
$N\!\approx\!500$ probe.

\paragraph{R1/R3: the format-vs-content ablation is underpowered / does
not resolve the mechanism.}
We agree, and we have stopped letting the abstract or
Section~\ref{sec:mechanism} imply otherwise. On Qwen3-8B all three arms
are zero-event---structured envelope with no list ($\mathrm{C}_{0.7}$,
$0/448$), envelope with a count-matched \emph{wrong} list
($\mathrm{C}_{0.8}$, $0/410$), and the real registry ($\mathrm{C}_1$,
$0/258$)---so we \emph{detect no content effect at this sample size}. We
now state plainly that this is absence of evidence, not evidence of
equivalence: the $\mathrm{C}_1\!-\!\mathrm{C}_{0.7}$ difference is bounded
by a Newcombe $95\%$ CI of $[-1.5,+1.4]$\,pp, consistent with the registry
content buying up to $\sim$1\,pp of recovery, not proof it buys nothing. A
format-over-content reading is offered as \emph{compatible with} the data
and is explicitly hedged. The decisive experiment---a powered ablation on
a high-event cell where the $\mathrm{C}_{0.8}$ decoy arm can actually
fabricate, so $\mathrm{C}_{0.8}$ vs $\mathrm{C}_1$ separates copying from
cueing---is in progress; we report no result for it here.

\paragraph{R3: only one benchmark (BFCL).}
We acknowledge the breadth limit and have built toward a second site
rather than asserting generality. A $\tau$-bench harness is wired
end-to-end through the same per-call TFR pipeline and has been
smoke-checked; a paper-ready gap test is underway and we make no
second-benchmark claim until the pass-rate and TFR numbers land. Until
then we scope every positive result to BFCL v4 multi-turn explicitly
(Section~\ref{sec:limitations}).

\paragraph{R1/R3: underpowered, zero-event-driven inferences.}
We have moved every zero-event cell onto exact bounds and away from
qualitative takeaways. The commercial frontier is reported as tight upper
bounds, not as ``proven zero'': Anthropic pools to $0/2{,}592$
($\leq\!0.14\%$, Clopper--Pearson $95\%$ two-sided) and OpenAI to
$0/2{,}117$ ($\leq\!0.18\%$). The RVR headline is the Fisher's exact
one-sided test on the pooled $20/1{,}417$ vs.\ $0/945$ contingency,
$p\!=\!3.5\!\times\!10^{-5}$, surviving Holm--Bonferroni
($p_{\mathrm{Holm}}\!=\!2.1\!\times\!10^{-4}$); we state that each per-tier
test is individually underpowered and report the per-tier $p$-values
($\{0.26,0.12,0.042,0.040\}$) so the pooling is auditable rather than
hidden. The Qwen3 ``collapse'' at $32$B is reported as
not-detected-at-this-$N$ ($0/224$, $\leq\!1.63\%$, an interval wide enough
to overlap the $14$B point estimate), not as emergent capability. The
Anthropic strict-pass non-inferiority test is reported as
\emph{undetermined} at $N\!=\!60$ ($1\!-\!\beta\!<\!0.30$), not as a pass.

\paragraph{R1/R2: confounded vendor comparison; RVR is a no-op on
frontier models.}
We do not claim to isolate the Anthropic--Qwen3 gap: parameter count,
training recipe, and provider guardrails co-vary, and commercial-vs-open
still bundles the serving path with the weights
(Section~\ref{sec:limitations}). What the controls above do remove from the
bundle is quantization (the gap survives at bf16) and Qwen-specificity (a
second lineage reproduces it). On practical impact, we agree RVR is a
call-path no-op where $\mathrm{TFR}\!=\!0$ and now recommend it
tier-conditionally---only on tiers with audited $\mathrm{TFR}\!>\!0$,
paired with executor-side allow-listing. The deployable takeaway is
narrowed accordingly: at this $N$ the structured envelope $\mathrm{C}_{0.7}$
alone drives the prevention, so a deployer can ship rejection without
echoing internal tool names and lose nothing detectable.

\paragraph{R1/R3: contamination is not ruled out.}
We do not claim it is. BFCL v4 predates every model tested, so the
commercial zero-event regime is observationally indistinguishable from
training-set contamination; we ran no paraphrase or membership-inference
control (Section~\ref{sec:limitations}). We therefore present the
commercial null as an upper bound under possible contamination, and note
that neither the open-weight non-zero band nor the RVR prevention depends
on the contamination question---a model that may well have seen BFCL and
still fabricates ($6.10\%$ on Qwen2.5-7B;
Section~\ref{sec:results:controls}) shows the probe is not merely
re-reading memorized registries.

\paragraph{R1/R3: reporting rough edges (acronym, denominators,
nomenclature).}
We swept these. The legacy ``TEHR'' acronym is gone; the metric is TFR
throughout, including every figure. The ablation figure now labels its
baseline denominator explicitly so the $9/615$ full-probe rate and the
matched-subset rate are no longer conflatable. ``Newcombe-hybrid TOST'' is
defined at first use against its code path, and the family for
Holm--Bonferroni (the three primary tests) is named in
Section~\ref{sec:setup}. No $p$-value appears without a script that
regenerates it; the harness ships $153$ unit tests and total API spend was
\$$82$.
