% Who Hallucinates Tools, How Often, and What Fixes It (formerly TEHR paper)
% SCALE @ ICML 2026 — anonymous double-blind submission

\documentclass{article}

% Recommended ICML 2026 packages
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xurl}  % allow long URLs to break across lines in references
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Camera-ready (SCALE-ICML 2026): [accepted] de-anonymizes + prints the notice.
\usepackage[accepted]{icml2026}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{xcolor}

% Listings setup for the RVR pseudocode in §3.
\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    showstringspaces=false,
    columns=fullflexible,
    frame=single,
    framerule=0.4pt,
    aboveskip=0.5em,
    belowskip=0.5em,
}

\icmltitlerunning{Who Hallucinates Tools, and What Fixes It}

\begin{document}

\twocolumn[
\icmltitle{Who Hallucinates Tools, How Often, and What Fixes It: \\
           A Per-Call Study Across Anthropic 4.x and Qwen3}

\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{S Akash}{aff1}
\icmlauthor{Shine Gupta}{aff1}
\end{icmlauthorlist}
\icmlaffiliation{aff1}{Indian Institute of Technology Patna, India}
\icmlcorrespondingauthor{S Akash}{drakathakash@gmail.com}

\icmlkeywords{tool-using agents, hallucination, function calling,
              BFCL, agent benchmarks, ICML 2026 SCALE}
\vskip 0.3in
]

\printAffiliationsAndNotice{}

\begin{abstract}
Tool-name hallucination is a known failure mode. Who actually does it,
how often, and what fixes it? We define a per-call Tool Fabrication
Rate (TFR) and run it on BFCL multi-turn against two
populations: five Anthropic 4.x versions across an eleven-month release
window, and the Qwen3-Instruct family at six sizes from $0.6$B to $32$B
(4-bit MLX). The Anthropic side is quiet. Across $2{,}592$
opaque-baseline calls we logged zero TFR events, Clopper--Pearson 95\%
two-sided upper bound $\leq\!0.14\%$. Commercial models across the OpenAI gpt-4.1
and gpt-4o tiers also log $0\%$ TFR ($0/2{,}117$ pooled, $\leq\!0.18\%$).
The open-weight Qwen3 family isn't quiet: it logs non-zero TFR, reaching
$10.4\%$ on the worst per-arm cell. And the invented calls are not
harmless: $70\%$ name state-changing actions carrying concrete arguments
(fabricated \texttt{place\_order} and \texttt{cancel\_booking} calls), so
under a permissive executor the failure is an unintended \emph{action},
not a failed lookup. We
propose Registry-Visible Reprompting (RVR), a
training-free middleware that, on a registry miss, returns one re-prompt
wrapping a structured \texttt{tool\_not\_found} envelope. RVR removes all
twenty pooled Qwen3 fabrications in the matched per-tier subset
(Fisher's exact one-sided, $p=3.5\!\times\!10^{-5}$ on $20/1{,}417$ vs.\
$0/945$). A secondary, deliberately hedged ablation asks where the fix
lives. Dropping the registry listing from the envelope
($\mathrm{C}_{0.7}$; $0/448$ on Qwen3-8B) and even filling it with
\emph{wrong} tool names ($\mathrm{C}_{0.8}$; $0/410$) both stay at zero,
matching the real list ($\mathrm{C}_1$; $0/258$). We do not read this as
proof that content is irrelevant: all three arms are zero-event, so this
is absence of evidence, not evidence of equivalence. At this sample size
we detect no content effect; the $\mathrm{C}_1\!-\!\mathrm{C}_{0.7}$
difference is bounded by a Newcombe 95\% CI of $[-1.5, +1.4]$~pp ---
consistent with content buying up to $\sim$1~pp, not proof it buys
nothing. On a high-event cell (Qwen2.5, $\mathrm{C}_0=6.10\%$) the
ablation is powered: a \emph{wrong} registry list recovers as well as the
real one ($\mathrm{C}_{0.8}$ vs.\ $\mathrm{C}_1$, Fisher $p=1.0$; both
$\sim\!24\times$ below baseline), so recovery is format-driven, echoing
Min et al.~\citep{min2022rethinking}. Descriptively, Qwen3's rate is non-monotone in scale,
climbing from $0\%$ at $0.6$B to $\mathbf{1.64\%}$ at $14$B and back to
$0\%$ at $32$B; six points are not a curve. A precision ladder
(4-bit/8-bit/bf16) shows the fabrication persists at full precision, so
it is not a quantization artefact, and a second open family
(Llama-3.1-8B) reproduces the gap.
On Anthropic's zero-event regime RVR also logs zero, but the strict-pass
subset slips at $N\!=\!60$; we recommend tier-conditional deployment.
\end{abstract}

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_method}
\input{sections/04_setup}
\input{sections/05_results}
\input{sections/06_mechanism}
\input{sections/07_limitations}

\bibliography{refs}
\bibliographystyle{icml2026}

\input{sections/08_llm_disclosure}
\input{sections/A1_appendix}

\end{document}
